\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-10-30 analysis/paper/paper.Rmd
methods - NEON data products and AOP

# Methods {-}
NEON data collection protocols
AOP flights
Plant mapping 
Network of sites and observations (how many? ecoclimatic domains? ecosystem coverage?
Figure \@ref(fig:fig-studyArea)

@@

We extracted hyperspectral data for all mapped stems at NEON sites using the neonhs [@neonhs] package. 
We assumed that plant locations did not change over time.

>>>>

# Methods {-}
The NEON data that we used for our study include both *in-situ* plant measurements and airborne remote sensing image data [@neonDataProducts].
The Woody Plant Vegetation Structure (data product code NEON.DP1.10098) includes individual plant locations along with species and genus observations that are collected every 1 to 3 years. 
The NEON Airborne Observation Platform (AOP) collects airborne remote sensing data regularly at NEON sites. There are three AOP payloads, each carrying three types of sensors: (1) a high-resolution digital camera to capture red, green, blue (RGB) true-color images, (2) a light detection and ranging (lidar) system to capture discrete and waveform lidar data with approximately 1-4 points/waveforms per square meter, and (3) a pushbroom-style imaging spectrometer (AVIRIS next-gen) to capture hyperspectral data. The hyperspectral data contains 426 narrow bands spanning the visible to shortwave infrared wavelengths, from 380 - 2500nm, and the image data products derived have a spatial resolution of 1m
The AOP flies at an altitude of 1000m above ground level and the flight season typically runs from May to October.

NEON sampling design
NEON data collection protocols 
AOP flights
Plant mapping 
Network of sites and observations (how many? ecoclimatic domains? ecosystem coverage?
Figure \@ref(fig:fig-studyArea)

@@

We extracted hyperspectral data for all mapped stems at NEON sites.

We assumed that plant locations did not change over time.
